Final Project Code ALL

### 2022-12-11 Draft_Final_Code.Rmd
Worked on Plots

```{r}
# Fit Models
set.seed(123) # make sure to run this before each fit so that you have the same 1000 trees
data_fit_mtry3 <- fit(data_wf_mtry3, data = imdb_clean_class)

@@

#### J Index vs. Distance

@@

@@

### Obtain Evaluation Metrics for Logistic Regression

```{r}
log_metrics <- metric_set(accuracy,sens,yardstick::spec)

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .25)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

We manually performed the hard predictions.

@@

imdb_hc_full <- imdb_clean %>%
  select(Gross, Budget) %>%
  filter(Budget != 0)

@@

```{r}
imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
imdb_full_avg <- hclust(dist_mat_full, method = "average")    # Full Data

@@

plot(imdb_hc_avg, labels = imdb_hc$Genre_1)

@@

plot(imdb_hc_avg, labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3))

@@

### Cutting the Tree

```{r}
imdb_clean_clust <- imdb_clean %>%
  filter(Budget != 0) %>%
    mutate(
        hclust_num = factor(cutree(imdb_full_avg, k = 3)) # Cut into 6 clusters (k)
    )
```

@@

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = hclust_num, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num)) +
    geom_point() +
    theme_classic()

imdb_clean_clust %>%
  count(hclust_num)

imdb_clean_clust %>%
  count(Genre_1)
```

>>>>

```{r}
# Fit Models
set.seed(123)
data_fit_mtry3 <- fit(data_wf_mtry3, data = imdb_clean_class)

@@

@@

#### Distance vs. Threshold

@@

### Obtain Evaluation Metrics for Logistic Regression Model with Thresholds

```{r}
# To determine final threshold

log_metrics <- metric_set(accuracy,sens,yardstick::spec)

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .78)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
    mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .71)) %>%
    log_metrics(truth = flop, estimate = .pred_class, event_level = 'second')

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .78)) %>%
  conf_mat(truth = flop, estimate = .pred_class)

final_output %>%
  mutate(.pred_class = make_two_class_pred(.pred_FALSE, levels(flop), threshold = .71)) %>%
  conf_mat(truth = flop, estimate = .pred_class)
```

@@

We manually performed the hard predictions with threshold = .78.

@@

imdb_hc_full <- imdb_clean %>%
  select(Gross, Budget) %>%
  filter(Budget > 1)

@@

### Perform Fusing Process

```{r}
imdb_hc_avg <- hclust(dist_mat_scaled, method = "average")    # Subset
imdb_full_avg <- hclust(dist_mat_full, method = "average")    # Full Data
```

@@

plot(imdb_hc_avg, labels = imdb_hc$Genre_1, main = "Movie Clusters", xlab = NULL)

@@

plot(imdb_hc_avg, 
     main = "Visualizing Movie Clusters",
     labels = paste(imdb_hc$Genre_1, imdb_hc$Genre_2, imdb_hc$Genre_3), 
     hang = -1, 
     cex = 1)

@@

### Cutting the Tree (Choosing k)

```{r}
imdb_clean_clust <- imdb_clean %>%
  filter(Budget > 1) %>%
    mutate(
        hclust_num2 = factor(cutree(imdb_full_avg, k = 2)), # Cut into 2 clusters (k)
        hclust_num4 = factor(cutree(imdb_full_avg, k = 4)), # Cut into 4 clusters (k)
        hclust_num8 = factor(cutree(imdb_full_avg, k = 8)) # Cut into 8 clusters (k)
    )
```

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
  geom_bar(position = "fill") +
  labs(x = "Cluster", 
       y = "Proportion of Cluster", 
       title = "Selecting Number of Clusters (k)") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

ggplot(imdb_clean_clust, aes(x = hclust_num4, fill = Genre_1)) +
  geom_bar(position = "fill") +
  labs(x = "Cluster", 
       y = "Proportion of Cluster", 
       title = "Selecting Number of Clusters (k)") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

ggplot(imdb_clean_clust, aes(x = hclust_num8, fill = Genre_1)) +
  geom_bar(position = "fill") +
  labs(x = "Cluster", 
       y = "Proportion of Cluster", 
       title = "Selecting Number of Clusters (k)") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))
```

@@

```{r}
ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = Genre_1)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = hclust_num2, fill = New_Genre)) +
    geom_bar(position = "fill") +
    labs(x = "Cluster") + 
    theme_classic()

ggplot(imdb_clean_clust, aes(x = Budget, y = Gross, color = hclust_num2)) +
  geom_point() +
  labs(x = "Budget in USD", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Visualizing Clusters: Gross Profit vs. Budget") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

ggplot(imdb_clean_clust, aes(x = hclust_num2, y = Budget)) +
  geom_boxplot() +
  labs(x = "Cluster", 
       y = "Budget in USD", 
       title = "Visualizing Clusters: Budget") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

ggplot(imdb_clean_clust, aes(x = hclust_num2, y = Gross)) +
  geom_boxplot() +
  labs(x = "Cluster", 
       y = "Gross Profit in USD (Log Scale)", 
       title = "Visualizing Clusters: Gross Profit") + 
  theme_classic() + 
  theme(plot.title = element_text(size = 20, face = "bold"))

imdb_clean_clust %>%
  count(hclust_num2)

imdb_clean_clust %>%
  group_by(hclust_num2) %>%
  summarize(mean(Gross), sd(Gross), min(Gross), max(Gross),
            mean((Budget/100000)), sd((Budget/100000)), min((Budget/100000)), max((Budget/100000)))
```
